Verifying Demonstrations

### 2018-05-23 paper/conclusions.tex
Adds discussion: cred renewal, deployment (fixes #86)

>>>>

As implied by the last statement, there is the problem of renewing credentials.
As with all identity cards, passports \etc, they have a limited lifetime and 
must be renewed at regular intervals.
The rate at which Alice is allowed to renew her credentials affects to what 
extent she can perform Sybil attacks.

Currently, the only problem preventing wide deployment is the lacking hardware 
in smartphones.
However, due to the rapid development of \enquote{smart} solutions, we believe 
this is only a matter of time.
\Eg mobile payments and public transport tickets that can be used over \ac{NFC} 
will eventually require \iac{DB} chip.
Without \ac{DB} for these applications, the user must manually confirm on the 
screen to prevent attacks.
We believe that the drive for increased usability will replace this type of 
confirmation by distance bounding.

The deployment of the needed credentials should not be a problem either.
There are already countries where national \ac{eID} systems are widely deployed.
The speed of adoption will depend on the architecture of these systems.
For instance, the system used in Sweden, BankID, is implemented in software and 
can thus be easily upgraded to include the anonymous credentials we need.
As for coverage of the population: more than \SI{95}{\%} of people in the ages 
21--50 uses BankID, it is \SI{88}{\%} for ages 51--60 and \SI{76}{\%} for ages 
61--70\footnote{%
  Official statistics, in Swedish:
  \url{https://www.bankid.com/assets/bankid/stats/2018/statistik-2018-04.pdf}.
}.

While the deployment of the necessary technologies are not yet available in 
authoritarian regimes, they are in several democracies.
We believe that it as important to implement systems such as ours to prevent any 
democracy of slipping down the slope towards dictatorship.
